### 2018-01-22 response_to_referee.txt

     The draft lacks of some important literature contextualization. A
     critical one is a recent Annual Review of Astronomy and
     Astrophysics entitled Markov Chain Monte Carlo Methods for
     Bayesian Data Analysis in Astronomy
     https://arxiv.org/abs/1706.01629

Yes, we know this paper. We now cite it near the end of the first
Section, and near the beginning of Section 10. We note in both places
that the Sharma review goes into much more depth on methods than we
do; our goals here are far more introductory.

     I would like the authors to please explain how their review
     brings something new to the literature, considering the amount of
     good and available material about MCMC.

Good point. We are slightly more explicit about this now in the
introductory section, in the paragraph starting "In what
follows...". The idea is to provide a getting-started user-manual for
MCMC conceptually or specifically, but not really review new
developments or sophisticated methods. It is more like we are trying
to specifically emphasize the importance of basic good pratices; we
say that more clearly now.

@@

     Bayesian Methods for the Physical Sciences: Learning from
     Examples in Astronomy and Physics, Springer Series in
     Astrostatistics, 2015 Andreon, and Weaver

     And

     Bayesian Models for Astrophysical Data: Using R, JAGS, Python,
     and Stan, Cambridge University press, Hilbe, de Souza and Ishida,
     2017

Good point; these are all now cited in the same "In what follows..."
paragraph, where we explain our difference from the rest of the
literature.

### 2018-01-22 mcmc.tex
item 1

In what follows, we are going to provide a kind of ``user manual'' or
advice document or folklore capture regarding the use of \MCMC\ for
data analysis.
This will not be a detailed description of multiple \MCMC\ methods
(indeed, we will only explain one method in detail), and it will not
be about the mathematical properties or structure of the method or
methods.\note{For a description of various different sampling methods,
  given from the point of view of an astrophysicist, see the review by
  \citet{sharma}. We say a bit about different \MCMC\ methods in
  \sectionname~\ref{sec:methods}, but our discussion is limited
  relative to Sharma's review.}
It will be about how to use \MCMC, including diagnosis and
trouble-shooting.

@@

There is no general, problem-independent solution for either of these
problems.
Indeed, there are many different strategies that work well or badly
for different functions $f(\pars)$.
In this \sectionname, we will try to guide the reader towards methods
that might help in different circumstances.
We will not give a full description of all the \MCMC\ algorithms out
there, but just provide some field notes and pointers to references.
New \MCMC\ methods are being developed all the time, so a reader with a
serious problem would do well to consult with the applied-mathematics
or statistics literature.\note{Your best interface to these
  literatures is often a colleague in another department, like applied
  mathematics, statistics, or computer science.  Break down those
  walls!}
The different methods to which we refer here are (in general) very
different in their difficulty of implementation.
We won't help with that either, except to say that there are more and
more open-source or distributed packages every year.
We will try to name some current implementations in the notes, but any
list compiled today will be incomplete tomorrow.\note{One check-point
  in this literature is the compilation volume by
  \citet{mcmchandbook}, but much has been developed and changed even
  since that was written.}
The spaces of \MCMC\ methods and \MCMC\ method implementations are both
growing rapidly, in part because \MCMC\ has become such a core
technology in the empirical sciences.

All we are going to do here is give a cursory mention to some methods
we know about, with some keywords that can be used to search more
deeply.
There is no sense in which this list is comprehensive; these are just
methods (or method classes) that are likely to be useful to projects
similar to projects we ourselves have executed.\note{There is a
  more in-depth and more comprehensive list of astrophyically relevant
  \MCMC\ methods in the review by \citet{sharma}.}

@@

@@

@@

>>>>

In what follows, we are going to provide a kind of ``user manual'' or
advice document or folklore capture regarding the use of \MCMC\ for
data analysis.
This will not be a detailed description of multiple \MCMC\ methods
(indeed, we will only explain one method in detail), and it will not
be about the mathematical properties or structure of the method or
methods.\note{For a description of various different sampling methods,
  given from the point of view of an astrophysicist, see the review by
  \citet{sharma}. We say a bit about different \MCMC\ methods in
  \sectionname~\ref{sec:methods}, but our discussion is limited
  relative to Sharma's review. For even more depth, there are relevant
  book-length treatments of \MCMC; our favorite is \citet{mcmchandbook}.
  There are also
  good books on Bayesian data analysis more generally that
  include discussion of \MCMC\ as a part of that;
  for example, \citet{kruschke}, and \citet{andreon} and \citet{hilbe}.}
Think of this \documentname\ as a getting-started document for a new user
of \MCMC\ methods.
It concentrates on conceptual points, and questions we get asked
frequently by users, with a concentration on how an \MCMC\ project is
diagnosed and tested, and how its outputs are used responsibly.
Most of what we say will
be applicable to any \MCMC\ method; in that sense the discussion is general.
And all in the language---more-or-less---of an astrophysicist.

@@

There is no general, problem-independent solution for either of these
problems.
Indeed, there are many different strategies that work well or badly
for different functions $f(\pars)$.
In this \sectionname, we will try to guide the reader towards methods
that might help in different circumstances.
We will not give a full description of all the \MCMC\ algorithms out
there, but just provide some field notes and pointers to references.
New \MCMC\ methods are being developed all the time, so a reader with a
serious problem would do well to consult with the applied-mathematics
or statistics literature.\note{Your best interface to these
  literatures is often a colleague in another department, like applied
  mathematics, statistics, or computer science.  Break down those
  walls!}
The different methods to which we refer here are (in general) very
different in their difficulty of implementation.
We won't help with that either, except to say that there are more and
more open-source or distributed packages every year.
We will try to name some current implementations in the notes, but any
list compiled today will be incomplete tomorrow.\note{One check-point
  in this literature is the compilation volume by
  \citet{mcmchandbook}, but much has been developed and changed even
  since that was written. For less in-depth but more current---and
  more astrophysically relevant---coverage, see also the review by \citet{sharma}.}
The spaces of \MCMC\ methods and \MCMC\ method implementations are both
growing rapidly, in part because \MCMC\ has become such a core
technology in the empirical sciences.

All we are going to do here is give a cursory mention to some methods
we know about, with some keywords that can be used to search more
deeply.
There is no sense in which this list is comprehensive; these are just
methods (or method classes) that are likely to be useful to projects
similar to projects we ourselves have executed.

@@

\bibitem[Andreon \& Weaver(2015)]{andreon}
  Andreon, S. \& Weaver, B., 2015,
  \textit{Bayesian Methods for the Physical Sciences: Learning from Examples in Astronomy and Physics},
  Springer
  \isbn{9783319152875}.

@@

\bibitem[Hilbe \etal(2017)]{hilbe}
  Hilbe, J. M., de~Souza, R. S., \& Ishida, E. E. O., 2017,
  \textit{Bayesian Models for Astrophysical Data: Using R, JAGS, Python, and Stan},
  \isbn{9781107133082}.

@@

\bibitem[Kruschke(2015)]{kruschke}
  Kruschke, J. K., 2015,
  \textit{Doing Bayesian Data Analysis: A Tutorial with R, JAGS, and Stan}, 2ed,
  Academic Press
  \isbn{9780124058880}.
